---
author: "an433"
date: "2023-02-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, out.width = "150px", echo=FALSE, out.extra='style="float:right; padding:5px"'}
url <- "https://gradschool.cornell.edu/wp-content/uploads/2022/05/Angela-Nankabirwa-crop-400x400.jpg"
knitr::include_graphics(url)
```


<center> 
# Angela Nankabirwa   
PhD, Ecology and Evolutionary Biology,  
Cornell University,  
*an433@cornell.edu*  
</center>


<br>

### *Employment*
**2021 to date:** Graduate Student, Cornell University

**2015 to 2021:** FIRRI, Uganda

<br>

### *Education*
**2021 to date:** PhD Ecology, Cornell University

**2018-2020:** Msc. Marine and Lacustrine Science and Management, Vrije Universite Brussel, Ghent University, Antwerp University  

<br>

### *Publications*

******************************************************

1. Nankabirwa. A., et al.,............. (2022)
2. Morelli, M., Theus, Marie, .....**in preparation**


### \hfill Conferences

+ IAGLR: African Great Lakes

    + Lake Victoria
    + Lake Edward

+ SFS: Freshwater research

    + Lake Superior


### <ins> *Hobbies* </ins>

===============================================

* Volleyball
* Music, dance and drama
* Nature  [*1*]{style="float:right"}




